---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dukecvd

<!-- badges: start -->
<!-- badges: end -->

## Overview

The goal of dukecvd is to generate visualizations with Duke's official suite of colors in a color blind friendly way. This package is integrated with ggplot2 and its visualization tools. 

## Installation


``` r
# Install dukecvd directly:
install.packages("dukecvd")

# Or alternatively, install development version from GitHub
# install.packages("devtools")
devtools::install_github("aidangildea/dukecvd")
```
## Usage

This package is fully integrated with ggplot2, and therefore, allows you to customize several visualization features. By adding aesthetic functions such as `theme_duke()` and `scale_color_duke()` to your visualizations, you can easily implement Duke official colors in a color blind friendly way.

For further information on how to use ggplot2, please visit its [GitHub repository](https://github.com/tidyverse/ggplot2).

## Example

First, create a standard ggplot2 visualization. In this example, we will use 
a scatter plot. 

```{r plot}
library(ggplot2)
library(dukecvd)
plot <- ggplot2::ggplot(iris, ggplot2::aes(Sepal.Length, Sepal.Width)) +
  ggplot2::geom_point(ggplot2::aes(colour = Species)) +
  ggplot2::labs(title = "Title", caption = "Caption", x = "X Var", y = "Y Var")

plot
```

Then, simply convert your visualization to Duke official colors by calling `theme_duke()`.

```{r themeduke}
plot + theme_duke()
```

## Questions

For further questions about this package and its use, please reach out to Aidan Gildea
at aidan.gildea@duke.edu.
