---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# duke

<!-- badges: start -->
<!-- badges: end -->

## Overview

**duke** allows users to generate visualizations with Duke's official suite of colors in a color blind friendly way. By using it alongside **ggplot2**, you can easily promote accessibility in the Duke community and beyond. 

## Installation

``` r
# Install duke directly:
install.packages("duke")

# Or alternatively, install development version from GitHub
# install.packages("devtools")
devtools::install_github("aidangildea/duke")
```
## Usage

This package is fully integrated with ggplot2, and therefore, allows you to customize several visualization features. Aesthetic functions such as [`theme_duke()`](https://aidangildea.github.io/duke/articles/theme_duke_vignette.html) and [`scale_color_duke()`](https://aidangildea.github.io/duke/articles/scale_duke_discrete_vignette.html) quickly make your graphs visually pleasing and accessible to your audience.

For further information on how to use ggplot2, please visit its [GitHub repository](https://github.com/tidyverse/ggplot2).

## Example

By using `duke` functions, you can easily convert your visualizations to Duke official colors.

```{r plot}
library(ggplot2)
library(duke)

plot <- ggplot2::ggplot(iris, ggplot2::aes(Sepal.Length, Sepal.Width)) +
  ggplot2::geom_point(ggplot2::aes(colour = Species)) +
  ggplot2::labs(title = "Sepal Length vs. Sepal Width", 
  caption = "Data sourced from iris in datasets package.", 
  x = "Sepal Length", y = "Sepal Width")

plot2 <- ggplot2::ggplot(iris, ggplot2::aes(Sepal.Length, Sepal.Width)) +
  ggplot2::geom_point(ggplot2::aes(colour = Sepal.Length)) +
  ggplot2::labs(title = "Sepal Length vs. Sepal Width", 
  caption = "Data sourced from iris in datasets package.", 
  x = "Sepal Length", y = "Sepal Width")
```

```{r themeduke}
plot + 
  theme_duke() +
  scale_duke_discrete()

plot2 + 
  theme_duke() +
  scale_duke_continuous()
```

## Questions

For further questions about this package and its use, please reach out to Aidan Gildea at aidan.gildea@duke.edu.
