---
title: "duke_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{duke_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = .618
)
```

```{r setup}
library(duke)
library(palmerpenguins)
library(ggmosaic)
library(ggplot2)
attach(penguins)
```

This vignette aims to comprehensively demonstrate the use and functionality of the package `duke`. `duke` is fully integrated with the `ggplot2` and allows for the creation of Duke official branded visualizations that are color blind friendly. 

## Scatter Plot - Continuous Color

```{r scatter c}
plot <- ggplot(palmerpenguins::penguins, aes(x=bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = body_mass_g)) +
  labs(title = "Bill Length vs. Bill Depth", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot + 
  scale_duke_continuous() +
  theme_duke()
  
plot + 
  geom_point(shape = species) +
  scale_duke_continuous() +
  theme_duke()

plot + 
  scale_duke_continuous() +
  theme_minimal()
```

## Scatter Plot - Discrete Color

```{r scatter d}
plot1 <- ggplot(palmerpenguins::penguins, aes(x=bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species)) +
  labs(title = "Bill Length vs. Bill Depth", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Bill Length (mm)", y = "Bill Depth (mm)")

ggplot(palmerpenguins::penguins, aes(x=bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species)) +
  theme_minimal() +
  labs(title = "Bill Length vs. Bill Depth", subtitle = "This is the subtitle", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot1 + 
  scale_duke_discrete() +
  theme_duke()

plot1 + 
  scale_duke_discrete() +
  theme_minimal()
```


## Bar Plot

```{r bar}
plot2 <- ggplot(palmerpenguins::penguins, aes(x=species, fill = species)) +
  geom_bar() +
  labs(title = "Distribution of Penguin Species", caption = "(Colors from left to right) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Species", y = "Count") +
  theme(legend.position = "none")

plot2 +
  scale_duke_discrete() +
  theme_duke()

plot2 + 
  scale_duke_discrete() +
  theme_minimal()
```

## Histogram

```{r hist}
plot3 <- ggplot2::ggplot(palmerpenguins::penguins, aes(body_mass_g)) +
  geom_histogram(ggplot2::aes(fill = species), alpha = 0.8) +
  labs(title = "Distribution of Penguin Body Mass", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Body Mass (g)", y = "Count")

plot3 + 
  scale_duke_discrete() +
  theme_duke()

plot3 + 
  scale_duke_discrete() +
  theme_minimal()
```

## Box Plot

```{r box}
plot4 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(sex, body_mass_g)) +
  ggplot2::geom_boxplot() +
  ggplot2::labs(title = "Comparison of Body Mass By Sex", x = "Sex", y = "Body Mass (g)")

plot4 + 
  theme_duke()

plot4 +
  theme_minimal()
```

## Density Plot

```{r density}
plot5 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(bill_depth_mm)) +
  ggplot2::geom_density(ggplot2::aes(fill = species)) +
  ggplot2::labs(title = "Density of Penguin Bill Depth", x = "Bill Depth (mm)", y = "Densiy")

plot5 + 
  scale_duke_discrete() +
  theme_duke()

plot5 + 
  scale_duke_discrete() +
  theme_minimal()
```

## Jitter Plot - Discrete Color

```{r jitter d}
plot6 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(year, body_mass_g)) +
  ggplot2::geom_jitter(ggplot2::aes(color = species)) +
  ggplot2::labs(title = "Comparison of Body Mass By Year", x = "Year", y = "Body Mass (g)")

plot6 + 
  scale_duke_discrete() +
  theme_duke()

plot6 + 
  scale_duke_discrete() +
  theme_minimal()
```
## Jitter Plot - Discrete Color

```{r jitter c}
plot6.1 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(year, body_mass_g)) +
  ggplot2::geom_jitter(ggplot2::aes(color = bill_length_mm)) +
  ggplot2::labs(title = "Comparison of Body Mass By Year", x = "Year", y = "Body Mass (g)")

plot6.1 + 
  scale_duke_continuous() +
  theme_duke()

plot6.1 + 
  scale_duke_continuous() +
  theme_minimal()
```


## Mosaic Plot 

```{r mosaic plot}
plot7 <- ggplot(data = palmerpenguins::penguins) +
  ggmosaic::geom_mosaic(aes(x=ggmosaic::product(sex, island), fill = sex)) +
  labs(title = "Penguin Sex vs. Island", x = "Island", y = "Penguin Sex", caption = "(Color from top to bottom) \n Granite, Duke Navy Blue, Duke Royal Blue")

plot7 +
  scale_duke_discrete() +
  theme_duke()

plot7 +
  scale_duke_discrete() +
  theme_minimal()

```

# Label Plot
```{r label}
plot8 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(bill_length_mm, bill_depth_mm, fill = island)) +
  ggplot2::geom_label(aes(label = island)) +
  ggplot2::labs(title = "Bill Length/Depth by Island", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot8 + 
  scale_duke_discrete() +
  theme_duke()

plot8 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Quantile Plot

```{r quantile}
plot9 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(bill_length_mm, bill_depth_mm, color = species)) +
  ggplot2::geom_quantile() +
  ggplot2::labs(title = "Bill Length/Depth Quantiles", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot9 + 
  scale_duke_discrete() +
  theme_duke()

plot9 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Area Plot
```{r area}
plot10 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(body_mass_g, fill = species)) +
  ggplot2::geom_area(stat = "bin") +
  ggplot2::labs(title = "Area of Body Mass Index", x = "BMI")

plot10 + 
  scale_duke_discrete() +
  theme_duke()

plot10 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Dot Plot

```{r dotpot}
plot11 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(body_mass_g)) +
  ggplot2::geom_dotplot(aes(fill=species)) +
  ggplot2::labs(title = "Dotplot of BMI", x = "BMI")

plot11 + 
  scale_duke_discrete() +
  theme_duke()

plot11 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Frequency Polynomial Plot

```{r freqplot}
plot12 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(body_mass_g)) +
  ggplot2::geom_freqpoly(aes(color=species)) +
  ggplot2::labs(title = "Frequency Polynomial Plot of BMI", x = "BMI")

plot12 + 
  scale_duke_discrete() +
  theme_duke()

plot12 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Column Plot

```{r colplot}
plot13 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(species, body_mass_g, color = species)) +
  ggplot2::geom_col() +
  ggplot2::labs(title = "BMI By Species of BMI", x = "Species", y = "BMI")

plot13 + 
  scale_duke_discrete() +
  theme_duke()

plot13 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Violin Plot

```{r violinplot}
plot14 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(species, body_mass_g, fill = species)) +
  geom_violin(scale = "area") +
  ggplot2::labs(title = "BMI By Species", x = "Species", y = "BMI")

plot14 + 
  scale_duke_discrete() +
  theme_duke()

plot14 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Count Plot

```{r countplot}
plot15 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(species, island, color = species)) +
  geom_count() +
  ggplot2::labs(title = "Species Count by Island", x = "Species", y = "Island")

plot15 + 
  scale_duke_discrete() +
  theme_duke()

plot15 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Step Plot

```{r stepplot}
plot16 <- ggplot2::ggplot(palmerpenguins::penguins, ggplot2::aes(year, body_mass_g, color = species)) +
  geom_step()
  ggplot2::labs(title = "BMI By Year", x = "Year", y = "BMI")

plot16 + 
  scale_duke_discrete() +
  theme_duke()

plot16 + 
  scale_duke_discrete() +
  theme_minimal()
```

# Coordinate Polar

```{r coordpol}
plot1 +
  facet_wrap(~species) +
  theme_bw() +
  scale_duke_discrete()
```

