---
title: "scale_duke_color_discrete()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scale_duke_color_discrete()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = .618
)
```

This vignette is intended to demonstrate the functionality of `scale_duke_color_discrete()`. The function allows users to utilize a discrete color scale of Duke official branding colors on ggplot2 visualizations. It is fully integrated with ggplot2 visualizations.

# Plot Examples

For these visualization, we will use the R dummy data set `palmerpenguins`.

```{r penguins}
# install.packages("palmerpenguins")
library(palmerpenguins)
library(duke)
library(ggplot2)
library(ggmosaic)
attach(penguins)
```

## Scatter Plot

```{r scatter plot}
plot <- ggplot(palmerpenguins::penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species)) +
  labs(title = "Bill Length vs. Bill Depth", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot +
  scale_duke_color_discrete()
```

## Jitter Plot

```{r jitter plot}
plot2 <- ggplot(palmerpenguins::penguins, aes(x = island, y = bill_depth_mm)) +
  geom_jitter(aes(color = species)) +
  labs(title = "Bill Length vs. Bill Depth", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot2 +
  scale_duke_color_discrete()
```

