---
title: "scale_duke_discrete()"
author: "Aidan Gildea"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scale_duke_discrete_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
   fig.width = 8,
  fig.asp = .618
)
```

This vignette is intended to demonstrate the functionality of `scale_duke_discrete()`. The function allows users to utilize a discrete color scale of Duke official branding colors on ggplot2 visualizations. It is fully integrated with ggplot2 visualizations.

# Plot Examples

For these visualization, we will use the R dummy data set `palmerpenguins`.

```{r penguins}
#install.packages("palmerpenguins")
library(palmerpenguins)
library(duke)
library(ggplot2)
library(ggmosaic)
attach(penguins)
```

## Using `scale_duke_discrete()` on bar plots

```{r bar plot}
plot <- ggplot(palmerpenguins::penguins, aes(x=species, fill = species)) +
  geom_bar() +
  labs(title = "Distribution of Penguin Species", caption = "(Colors from left to right) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Species", y = "Count") +
  theme(legend.position = "none")

plot +
  scale_duke_discrete()
```

## Using `scale_duke_discrete()` on mosaic plots 

```{r mosaic plot}
plot2 <- ggplot(data = palmerpenguins::penguins) +
  ggmosaic::geom_mosaic(aes(x=product(sex, island), fill = sex)) +
  labs(title = "Penguin Sex vs. Island", x = "Island", y = "Penguin Sex", caption = "(Color from top to bottom) \n Granite, Duke Navy Blue, Duke Royal Blue")

plot2 +
  scale_duke_discrete()
```
## Using `scale_duke_discrete()` on scatter plots 

```{r scatter plot}
plot3 <- ggplot(palmerpenguins::penguins, aes(x=bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species)) +
  labs(title = "Bill Length vs. Bill Depth", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Bill Length (mm)", y = "Bill Depth (mm)")

plot3 + 
  scale_duke_discrete()
```
## Using `scale_duke_discrete()` on histogram plots 

```{r histogram}
plot4 <- ggplot2::ggplot(palmerpenguins::penguins, aes(body_mass_g)) +
  geom_histogram(ggplot2::aes(fill = species), alpha = 0.8) +
  labs(title = "Distribution of Penguin Body Mass", caption = "(Colors used) \n Duke Royal Blue, Duke Navy Blue, Copper", x = "Body Mass (g)", y = "Count")

plot4 + scale_duke_discrete()
```

